\section{Introduction}

The following document outlines the proposal for Chile-based AURA employees to provide out of hours technical support to Rubin's infrastructure.
This includes assisting the observatory through unexpected technical issues during on-sky nighttime observations.
Out of hours support includes events triggered before or after the standard working hours in Chile, also known as the ``day shift''.
Specifically, out of hours support starts on weekdays at 17:30 and ends the following day at 8:30, and spans the entire 24 hours of weekends and holidays.

%Types of employees who may be assisting with on-sky out of hours support:
%\begin{itemize}
%    \item AURA staff in Chile who are Chilean (exempt) <== addressed in document 
%    \item AURA staff in Chile who are not Chilean "expats" (exempt)
%    \item Chilean union staff in Chile (non-exempt) (are they also called "contractors"?) ** absolutely needed **
%    \item DOE staff in Chile (exempt) Are there Chileans in this category?
%    \item DOE not in Chile (exempt)
%    \item AURA not in Chile, mostly USA (exempt)
%    \item AURA not in Chile contractors (non-exempt) - not sure if these will be in the loop
%    \item Non-AURA not in Chile (3rd party institutions UW, Princeton, Madison, etc.) paid by AURA (exempt)
%    \item In-Kind (not paid by AURA) 
%\end{itemize}

The following classification of employees will be assisting with on-sky out of hours support:

\begin{longtable} {p{0.45\textwidth} p{0.2\textwidth} p{0.35\textwidth}} \hline

\textbf{Type of Employee} & \textbf{Exempt or \newline Non-Exempt} & \textbf{Notes}  \\\hline

AURA staff in Chile who are Chilean & Exempt &  Addressed in document   \\\hline
Chilean union staff in Chile (also called ``contractors'') & Non-Exempt & Absolutely needed for out of hours support;  not addressed in this document due to "pacto" agreement needs and max 2hr/day (10hr/week) overtime rules.  \\\hline
AURA staff in Chile who are not Chilean, aka "expats" & Exempt &  \\\hline
DOE staff in Chile & Exempt & Question: Are there Chileans in this category?  \\\hline
DOE staff not in Chile & Exempt &  \\\hline
AURA staff not in Chile, mostly USA & Exempt & \\\hline
AURA staff not in Chile contractors & Non-Exempt & Note: Not sure if these will be at the summit for out of hours support \\\hline
Non-AURA staff not in Chile (3rd party institutions UW, Princeton, Madison, etc.) paid by AURA & Exempt &  \\\hline
In-Kind & N/A \newline(not paid by AURA) \\\hline


\end{longtable}

This document covers the Rubin AURA exempt Chilean workers with respect to compensation for out of hours support (first row of the the table above).
Arrangements also need to be considered for row number 2, Chilean union staff in Chile (also called ``contractors''), who will be vital for commissioning.

On-call compensation is 10\% times the hourly wage for the duration of an official on-call shift.  
This increases to 100\% times the hourly wage if the person is called to work out of hours time Mondays through Saturdays (and 200\% on Sundays and holidays).

AURA/DOE/3rd-Party non-Chilean exempt employees are permitted to work out of hours, as long as the hours keep to the timecard allotment of 80 hours per two-week time period.  
Non-Chilean exempt employees do not receive hourly compensation for working overtime.
The compensation aspects in this document do not apply to non-Chilean employees who will be providing out of hours support, rows 3+ in the table above.